---
title: 'Data Sources'
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
    css: style.css

---

```{r, include = FALSE} 
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = '#>'
)

library(tidyverse)

data <- read.csv('../Data/sources.csv') %>%
  remove_rownames() %>% 
  column_to_rownames('Name')

```

Below is a record of the data products synthesised during MiMeMo. I've kept track of the structure of the data to make it easier to quickly check what we have. This will also function as a README for anyone else who follows and wants signposting to sources, or to know what additional data could be downloaded. 

```{r overlap, echo = FALSE, message = FALSE, warning = FALSE, fig.align='center'} 

overlap <- read.csv('../Data/sources.csv') %>% 
  mutate(From = as.Date(From, format = "%d/%m/%Y"),
         To = as.Date(To, format = "%d/%m/%Y")) %>% 
  arrange(From) %>%                                    # First sort by val. This sort the dataframe but NOT the factor levels
  mutate(Name = factor( Name, levels = Name))          # This trick update the factor levels


ggplot(overlap) +
  geom_segment(aes(x = From, xend = To, y = Name, yend = Name)) +
  theme_minimal() +
  labs(x = "Time period", y = "Source")

```


# NEMO-MEDUSA

### Light                   {.tabset} 

Shortwave surface Irradiance inputs to NEMO-MEDUSA.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

`r data['DRIVER-Lit', 'Source']`

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['DRIVER-Lit', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['DRIVER-Lit', 'From']`. 
* *To* `r data['DRIVER-Lit', 'To']`.
* *In* `r data['DRIVER-Lit', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['DRIVER-Lit', 'Files']`
* `r data['DRIVER-Lit', 'Memory']`
* `r data['DRIVER-Lit', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['DRIVER-Lit', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group'></i>  Spatial vars

<br>

`r data['DRIVER-Lit', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['DRIVER-Lit', 'Other_variables']`

<br>

---


### Air Temperature         {.tabset} 

Surface air temperatures as inputs to NEMO-MEDUSA.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

`r data['DRIVER-Tmp', 'Source']`

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['DRIVER-Tmp', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['DRIVER-Tmp', 'From']`. 
* *To* `r data['DRIVER-Tmp', 'To']`.
* *In* `r data['DRIVER-Tmp', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['DRIVER-Tmp', 'Files']`
* `r data['DRIVER-Tmp', 'Memory']`
* `r data['DRIVER-Tmp', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['DRIVER-Tmp', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

`r data['DRIVER-Tmp', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['DRIVER-Tmp', 'Other_variables']`

<br>

---


### Rivers                  {.tabset} 

Freshwater inputs to NEMO-MEDUSA.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

`r data['DRIVER-Riv', 'Source']`

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['DRIVER-Riv', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['DRIVER-Riv', 'From']`. 
* *To* `r data['DRIVER-Riv', 'To']`.
* *In* `r data['DRIVER-Riv', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['DRIVER-Riv', 'Files']`
* `r data['DRIVER-Riv', 'Memory']`
* `r data['DRIVER-Riv', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['DRIVER-Riv', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

`r data['DRIVER-Riv', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['DRIVER-Riv', 'Other_variables']`

<br>

---

### Model output            {.tabset} 

NEMO-MEDUSA model **OUTPUTS** for multiple Variables.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

`r data['NEMO-MEDUSA', 'Source']`

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['NEMO-MEDUSA', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['NEMO-MEDUSA', 'From']`. 
* *To* `r data['NEMO-MEDUSA', 'To']`.
* *In* `r data['NEMO-MEDUSA', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['NEMO-MEDUSA', 'Files']`
* `r data['NEMO-MEDUSA', 'Memory']`
* `r data['NEMO-MEDUSA', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['NEMO-MEDUSA', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

❗ Note, these matrices are different for velocity files (cell corners not centres). The grid otherwise appears the same. 

❗ Note, grid_W files contain different depths for layers.

`r data['NEMO-MEDUSA', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['NEMO-MEDUSA', 'Other_variables']`

<br>

---


# Other Ecological Drivers
### GEBCO                   {.tabset} 

Global terrain model for ocean and land at 15 arc-second intervals.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

[Downloaded from GEBCO.net](`r data['GEBCO', 'Source']` 'Click to visit the page')

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['GEBCO', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['GEBCO', 'From']`. 
* *To* `r data['GEBCO', 'To']`.
* *In* `r data['GEBCO', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['GEBCO', 'Files']`
* `r data['GEBCO', 'Memory']`
* `r data['GEBCO', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['GEBCO', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

`r data['GEBCO', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['GEBCO', 'Other_variables']`

<br>

---

### NGU                     {.tabset} 

Sediment classes in the Barents Sea, an overview document of likely bottom types from expert synthesis of multiple data sets ('SEABED SEDIMENTS (GRAIN SIZE), N750 OVERVIEW').

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

[Downloaded from NGU](`r data['NGU', 'Source']` 'Click to visit the page')

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['NGU', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['NGU', 'From']`. 
* *To* `r data['NGU', 'To']`.
* *In* `r data['NGU', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['NGU', 'Files']`
* `r data['NGU', 'Memory']`
* `r data['NGU', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['NGU', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

`r data['NGU', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['NGU', 'Other_variables']`

<br>

---

### ECMWF                   {.tabset} 

Significant wave height and direction from the CERA-20C 'Ocean Wave Synoptic Monthly Means'.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

[Downloaded from the ECMWF app](`r data['ECMWF', 'Source']` 'Click to visit the page')

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

*I downloaded the Northern hemisphere only.*

`r data['ECMWF', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['ECMWF', 'From']`. 
* *To* `r data['ECMWF', 'To']`.
* *In* `r data['ECMWF', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

*I only downloaded as far back as 2000.*

* `r data['ECMWF', 'Files']`
* `r data['ECMWF', 'Memory']`
* `r data['ECMWF', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['ECMWF', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

*Located within netcdf dims, not as variables.*

`r data['ECMWF', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

*Additional variables are available, but have not been downloaded from the web portal.*

`r data['ECMWF', 'Other_variables']`

<br>

---

### SINMOD                  {.tabset} 

Tidally resolved water velocity fields in the Arctic. Numerical ocean model output.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

`r data['SINMOD', 'Source']`

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['SINMOD', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['SINMOD', 'From']`. 
* *To* `r data['SINMOD', 'To']`.
* *In* `r data['SINMOD', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['SINMOD', 'Files']`
* `r data['SINMOD', 'Memory']`
* `r data['SINMOD', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['SINMOD', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

`r data['SINMOD', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['SINMOD', 'Other_variables']`

<br>

---

### Global NEWS             {.tabset} 

'Global Nutrient Export from Watersheds'. Modeled N and P input to oceans from rivers.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

[Downloaded from DANS](`r data['Global NEWS', 'Source']` 'Click to visit the page')

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['Global NEWS', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['Global NEWS', 'From']`. 
* *To* `r data['Global NEWS', 'To']`.
* *In* `r data['Global NEWS', 'By']`.
* *Duration* Updated annually.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['Global NEWS', 'Files']`
* `r data['Global NEWS', 'Memory']`
* `r data['Global NEWS', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['Global NEWS', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

`r data['Global NEWS', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['Global NEWS', 'Other_variables']`

<br>

---

### Arctic GRO              {.tabset} 

'Arctic Great Rivers Observatory'. Water quality field recordings from the 6 largest Arctic rivers.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

[Downloaded from arcticgreatrivers.org](`r data['Arctic GRO', 'Source']` 'Click to visit the page')

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['Arctic GRO', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['Arctic GRO', 'From']`. 
* *To* `r data['Arctic GRO', 'To']`.
* *In* `r data['Arctic GRO', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['Arctic GRO', 'Files']`
* `r data['Arctic GRO', 'Memory']`
* `r data['Arctic GRO', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['Arctic GRO', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

`r data['Arctic GRO', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['Arctic GRO', 'Other_variables']`

<br>

---


### Globcolour              {.tabset} 

Suspended particulate matter from binned monthly satellite colour data.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

Downloaded across an FTP connection. The code below should automatically do this for you, but you will need to get your own
username and password from Globcolour, and replace this in the script.

```{r code Globcolour download, eval = FALSE, warning= FALSE}
  
## Automate the downloading of supsended particulate matter from GloColour server

#### Set up ####

rm(list=ls())

library(tidyverse)
library(RCurl)

download <- function(Source, File) {
 
  Sys.sleep(pause)                                    # Pause so we're not locked out
 
  download.file(url = paste0(Source, File), destfile = paste("./Data/SPM/", File))
 
}              # Create path, download, and specify destination file name

url <- "ftp://ftp.hermes.acri.fr/GLOB/merged/month/"  # Path to directory of interest

userpwd <- "ftp_gc_*******:*******"                   # Your username and password

pause <- 120                                          # How long to leave between requests to the server
 
#### Build folder structure and download SPM files ####

files <- getURL(url, userpwd = userpwd, ftp.use.epsv = F, dirlistonly = T) %>% # List the sub-directories for years
  strsplit("\n") %>%                                  # Seperate names into individual entries
  map(function(x) paste0(url, x,"/")) %>%             # Create a full path for each subdirectory found
  unlist() %>%                                        # Strip back to a vector of yearly subdirectories
  map(~ {                                             # For each year folder
 
  Sys.sleep(pause)                                    # Pause so we're not locked out
 
  url <- .x                                           # Rememeber the name of this folder
  print(url)
 
  months <- getURL(.x, userpwd = userpwd, ftp.use.epsv = F, dirlistonly = T) %>% # Check which months are reported this year
  strsplit("\n") %>%                                  # Seperate names again
  map(function(x) paste0(url, x,"/01/")) %>%          # Create full paths for each source/year/month paths
  unlist()
  })  %>%                                   # How many months are in each year folder? pause so I'm not locked out
  unlist() %>%
  map(~ {
 
  Sys.sleep(pause)                                    # Pause between checking each folder to stop getting locked out
 
  url <- .x                                           # Remember the route to this subdirectory
  print(url)
 
  files <- getURL(.x, userpwd = userpwd, ftp.use.epsv = F, dirlistonly = T) %>% # Which files are in here?
  strsplit("\n") %>%                                  # Separate files
  map(function(x) paste0(url, x)) %>%                 # Create full path for each of these files
  unlist() %>%                                        
  as.data.frame(col.names = "Files") %>%              # Get a dataframe of all file names
  filter(grepl(".nc", `.`, fixed = TRUE)) %>%         # Limit to netcdf files
  filter(grepl("SPM", `.`, fixed = TRUE)) %>%         # Limit to suspended particulate matter files
  filter(grepl("L3b", `.`, fixed = TRUE))             # Limit to files on their Binned grid (high resolution I think)
   }) %>%                                             # Which files are in each folder? with a pause so I'm not locked out
  bind_rows() %>%                                     # Bind file names into dataframe
  rename(value = 1) %>%
  separate(value, into = c("Source", "File"), sep = "L3b_") %>% # Isolate file name to use when saving files
  mutate(File = paste0("L3b_", File),                 # Replace dropped separator
         Source = str_replace(Source, "ftp.hermes", paste0(userpwd,"@ftp.hermes"))) # Add password into link request
 
pmap(files, download)                                 # Download all the files, don't parallelise, we don't want to overload the server!

```

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['Globcolour', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['Globcolour', 'From']`. 
* *To* `r data['Globcolour', 'To']`.
* *In* `r data['Globcolour', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['Globcolour', 'Files']`
* `r data['Globcolour', 'Memory']`
* `r data['Globcolour', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['Globcolour', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

`r data['Globcolour', 'Spatial_variables']`

Two dimensions are also required:

* 'bin', id for a pixel
* 'row', the row in the grid for a pixel.

To get to coordinates in latitude and longitude:

```{r code Globcolour coordinates, eval = FALSE, warning= FALSE}
  index <- row[bin] - row[1]+1 
  lat_bin = center_lat[index]
  lon_bin = center_lon[index] + col[bin] * lon_step[index]
```

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

*Additional variables are available, but have not been downloaded from the server.*

`r data['Globcolour', 'Other_variables']`

<br>

---


### EMEP                    {.tabset} 

Modelled atmospheric deposition of reduced and oxidised Nitrogen from EMEP MSC-W.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

Downloaded from the EMEP server. The code below should automatically do this for you.

```{r code EMEP download, eval = FALSE, warning= FALSE}
  
## Automate the downloading of N atmospheric depostion data from EMEP server

library(tidyverse)
library(rvest)

download <- function(file) {
 
  download <- download.file(url = paste0(source, file), destfile = paste("./Data/EMEP Atmosphere/", file))
 
}                                                # Create path, download, and specify destination file name

source <- "https://thredds.met.no/thredds/fileServer/data/EMEP/2018_Reporting/" # Where are the files stored?

read_html("https://thredds.met.no/thredds/catalog/data/EMEP/2018_Reporting/catalog.html") %>% # Import the file catalog
  html_nodes("a") %>%                                                           # Extract links
  html_attr("href") %>%                      
  .[which(grepl("month", .), )] %>%                                             # Limit to monthly files
  str_remove(., fixed("catalog.html?dataset=EMEP/2018_Reporting/")) %>%         # Extract file names from links
  map(download)                                                                 # Download all the files, don't parallelise, we don't want to overload the website!


```

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['EMEP', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['EMEP', 'From']`. 
* *To* `r data['EMEP', 'To']`.
* *In* `r data['EMEP', 'By']`.
* *Duration* Updated annually.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['EMEP', 'Files']`
* `r data['EMEP', 'Memory']`
* `r data['EMEP', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['EMEP', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

*Located within netcdf dims, not as variables.*

`r data['EMEP', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

*Additional variables are available, but have not been downloaded from the web portal.*

`r data['EMEP', 'Other_variables']`

<br>

---

# Fishing
### Global Fishing Watch    {.tabset} 

Fishing effort from anonymised VMS signals and a model of vessel movement patterns.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

[Downloaded from Global Fishing Watch.](`r data['GFW', 'Source']` 'Click to visit the page')

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['GFW', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['GFW', 'From']`. 
* *To* `r data['GFW', 'To']`.
* *In* `r data['GFW', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['GFW', 'Files']`
* `r data['GFW', 'Memory']`
* `r data['GFW', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['GFW', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

`r data['GFW', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['GFW', 'Other_variables']`

<br>

---

### ICES                    {.tabset} 

International report on fisheries landings by species and country.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

`r data['ICES', 'Source']`

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['ICES', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['ICES', 'From']`. 
* *To* `r data['ICES', 'To']`.
* *In* `r data['ICES', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['ICES', 'Files']`
* `r data['ICES', 'Memory']`
* `r data['ICES', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['ICES', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

`r data['ICES', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['ICES', 'Other_variables']`

<br>

---


### IMR                     {.tabset} 

Reports of landings and effort by species and gear of Norwegian vessels.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

`r data['IMR', 'Source']`

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['IMR', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['IMR', 'From']`. 
* *To* `r data['IMR', 'To']`.
* *In* `r data['IMR', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['IMR', 'Files']`
* `r data['IMR', 'Memory']`
* `r data['IMR', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['IMR', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

`r data['IMR', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['IMR', 'Other_variables']`

<br>

---

### Rafisklaget             {.tabset} 

'The raw fish sellers society of Norway'. Value and weight of exploited species sold in different regions of Norway.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

[Downloaded from rafisklaget](`r data['rafisklaget', 'Source']` 'Click to visit the page')

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['rafisklaget', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['rafisklaget', 'From']`. 
* *To* `r data['rafisklaget', 'To']`.
* *In* `r data['rafisklaget', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['rafisklaget', 'Files']`
* `r data['rafisklaget', 'Memory']`
* `r data['rafisklaget', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['rafisklaget', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

`r data['rafisklaget', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['rafisklaget', 'Other_variables']`

<br>

---



### STECF Effort            {.tabset} 

Reports of effort by gear for EU vessels.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

[Downloaded from the europa portal](`r data['STECF-eff', 'Source']` 'Click to visit the page')

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['STECF-eff', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['STECF-eff', 'From']`. 
* *To* `r data['STECF-eff', 'To']`.
* *In* `r data['STECF-eff', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['STECF-eff', 'Files']`
* `r data['STECF-eff', 'Memory']`
* `r data['STECF-eff', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['STECF-eff', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

`r data['STECF-eff', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['STECF-eff', 'Other_variables']`

<br>

---

### STECF Landings          {.tabset} 

Reports of landings by species and gear for EU vessels.

#### <i class='fa fa-download' aria-hidden='true' style ='color:#003399;'></i>  Source

<br>

[Downloaded from the europa portal](`r data['STECF-ton', 'Source']` 'Click to visit the page')

<br>

---

#### <i class='fa fa-globe' aria-hidden='true' style ='color:#003399;'></i>  Space

<br>

`r data['STECF-ton', 'Space']`. 

<br>

---

#### <i class='fa fa-stopwatch' aria-hidden='true' style ='color:#003399;'></i>  Time

<br>

* *From* `r data['STECF-ton', 'From']`. 
* *To* `r data['STECF-ton', 'To']`.
* *In* `r data['STECF-ton', 'By']`.

<br>

---

#### <i class='fa fa-folder' aria-hidden='true' style ='color:#003399;'></i> File structure

<br>

* `r data['STECF-ton', 'Files']`
* `r data['STECF-ton', 'Memory']`
* `r data['STECF-ton', 'File_description']`

<br>

---

#### <i class='fa fa-eye' aria-hidden='true' style ='color:#003399;'></i>  Target vars

<br>

`r data['STECF-ton', 'Target_variables']`

<br>

---

#### <i class='fas fa-layer-group' aria-hidden='true' style ='color:#003399;'></i>  Spatial vars

<br>

`r data['STECF-ton', 'Spatial_variables']`

<br>

---

#### <i class='fa fa-plus' aria-hidden='true' style ='color:#003399;'></i>  other vars

<br>

`r data['STECF-ton', 'Other_variables']`

<br>

---
