---
title: "Script Runtimes"
date: "last updated: 12/02/2021"
output:
  html_document:
    css: style.css

---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  out.width = "100%",
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.asp = 1)

library(tidyverse) 

```

The figure below illustrates the run times for each of the MiMeMo scripts. Scripts are loosely classified into families - *bathymetry* - *fish* - *flows* - *NM* - *Sediment* - *StrathE2E*. These can all be run from a master script. The times are saved out automatically for batch processing, but this page accesses a saved record as I don't always run everything at once. Most data processing is fast (minutes) however processing NEMO-MEDUSA model output can take hours. The constraint on time is transferring the data from the idrive to the machine creating the summaries. For a student with a laptop and an external hard drive this can take all day. For my desktop wired to the server it's 2-3 hours. When files are stored locally on my machine it indicates all the data could be process in 20 minutes. 

```{r code runtimes, eval = TRUE}

timings <- readRDS("../Objects/All run times.rds") %>% 
  separate(Type, into = c(NA, "Type"), sep = "/")                             # Drop script folder

#### Cool circular bar plot ####

#Create dataset
data <- data.frame(
  individual= timings$Script,
  group= timings$Type,
  value= timings$Minutes) %>% 
  separate(individual, into = c(NA, "individual",NA), sep = "[.]") # Drop leading script family for labelling bars.

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 3
to_add <- data.frame( matrix(NA, empty_bar*nlevels(data$group), ncol(data)) )
colnames(to_add) <- colnames(data)
to_add$group <- rep(levels(data$group), each=empty_bar)
data <- rbind(data, to_add)
data <- data %>% arrange(group)
data$id <- seq(1, nrow(data))

# Get the name and the y position of each label
label_data <- data
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /(number_of_bar+1)     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0). I also add a bar for the y axis labels.
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

# prepare a data frame for base lines
base_data <- data %>% 
  group_by(group) %>% 
  summarize(start=min(id), end=max(id)) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

# Make the plot
ggplot(data, aes(x=as.factor(id), y=value, fill=group)) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  
  geom_bar(aes(x=as.factor(id), y=value, fill=group), stat="identity", alpha=0.5, colour = NA) +   # Begin plot
  # Add axis marks
  annotate("rect", xmin = 0.5, ymin = 0, xmax = max(data$id) + 1.5, ymax = 60, colour = "white", alpha=0.1, fill = "cornflowerblue") +
  annotate("rect", xmin = 0.5, ymin = 60, xmax = max(data$id) + 1.5, ymax = 120, colour = "white", alpha=0) +
  annotate("rect", xmin = 0.5, ymin = 120, xmax = max(data$id) + 1.5, ymax = 180, colour = "white", alpha=0.1, fill = "cornflowerblue") +
  annotate("rect", xmin = 0.5, ymin = 180, xmax = max(data$id) + 1.5, ymax = 240, colour = "white", alpha=0) +
  annotate("rect", xmin = 0.5, ymin = 240, xmax = max(data$id) + 1.5, ymax = 300, colour = "white", alpha=0.1, fill = "cornflowerblue") +
  # Add text labels for axis marks
  annotate("text", x = rep(max(data$id)+ 1, 5), y = c(60, 120, 180, 240, 300), 
           label = c("1", "2", "3", "4", "5") , color="grey", size=3 , angle=0, fontface="bold", hjust= 0.5) +
  geom_bar(aes(x=as.factor(id), y=value, fill=group), colour = "black", size = 0.3, stat="identity") +
scale_fill_manual(values = c("bathymetry" = "#ff8000",
                             "fish" = "#00ffff",
                             "flows" = "#0993de",    
                             "nemo-medusa" = "#FFFFFF",       
                             "saltless" = "#ffea09",   
                             "strathE2E" = "#aba6a6")) +
  ylim(-300,600) +          # More - creates more space in the centre, if a bar is larger than max it won't display
  annotate("text", x = max(data$id), y = 400, label = paste0("Total project run time: ", round(sum(data$value, na.rm = T)/60, digits = 2), " hours"), size = 3, hjust = 0) +
  theme_minimal() +
  theme(legend.position = c(0.5, 0.5),
        axis.text = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        plot.margin = unit(c(-4, -2.5,-2.5,-2.5), "cm")
       ) +
  coord_polar() + 
  geom_text(data=label_data, aes(x=id, y=value+45, label=individual, hjust=hjust), color="black", fontface="bold",alpha=0.6, size=2.5, angle= label_data$angle, inherit.aes = FALSE ) +
  # Add base line information
  geom_segment(data=base_data, aes(x = start, y = -30, colour = group, xend = end, yend = -30), 
               size=3.5 , inherit.aes = FALSE, show.legend = FALSE)  +
scale_colour_manual(values = c("bathymetry" = "#ff8000",
                             "fish" = "#00ffff",
                             "flows" = "#0993de",    
                             "nemo-medusa" = "#FFFFFF",       
                             "saltless" = "#ffea09",   
                             "strathE2E" = "#aba6a6")) +
    labs(fill = NULL) +
 # labs(caption = paste0("Total project run time: ", round(sum(data$value, na.rm = T)/60, digits = 2), " hours")) +
  NULL


```
