---
output: 
  html_document:
pagetitle: "Workflow"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse) 
library(visNetwork)

```

# Script dependencies

The widget below illustrates the hierarchy for MiMeMo scripts. It's interactive, so feel free to zoom in, drag the view, and highlight a script by clicking on a node. You can also move the nodes. When a script is highlighted, so are others within 1 degree of separation (scripts immediately upstream and downstream in the pipeline). You can also highlight a specific script from the drop down menu. Nodes are colour coded by family, and layers in the hierarchy indicate how many scripts must be run in advance. 

The network is created programmaticaly by looking for shared objects across all scripts. This is evaluated by searching the code for calls to functions such as `saveRDS` and `readRDS`. 

```{r code relations, echo = FALSE, eval = TRUE, warning= FALSE}

network <- readRDS("./Objects/network.rds")

#### Build network widget ####

v <-palettetown::ichooseyou("charizard", length(unique(network[[2]]$group))) # get colours for each group

visNetwork(network[[2]], network[[1]], width = "100%", height = "800") %>%   # Build the network
  visHierarchicalLayout(direction = "UD") %>%                                # Use hierarchical layout from top to bottom
  visLegend(width = 0.15, ncol = 1, zoom = FALSE) %>%                        # Add a legend
  visOptions(highlightNearest = list(enabled = TRUE, labelOnly = FALSE),     # Control highlighting when selecting script
             nodesIdSelection = TRUE, clickToUse = TRUE, selectedBy = "group") %>% # Add drop down menu to highlight scripts
  
  ## Control colouring and highlighting per group
  

  visGroups(groupname = "bathymetry", shape = "dot", color = list(background = v[1], border = v[1], 
                                              highlight = list(background = "white", border = v[1]))) %>%
  visGroups(groupname = "fish", shape = "dot",color = list(background = v[2], border = v[2],
                                              highlight = list(background = "white", border = v[2]))) %>% 
  visGroups(groupname = "flows", shape = "dot", color = list(background = v[3], border = v[3],
                                              highlight = list(background = "white", border = v[3]))) %>% 
  visGroups(groupname = "nemo-medusa", shape = "dot", color = list(background = v[4], border = v[4],
                                              highlight = list(background = "white", border = v[4]))) %>% 
  visGroups(groupname = "saltless", shape = "dot", color = list(background = v[5], border = v[5],
                                              highlight = list(background = "white", border = v[5]))) %>% 
  visGroups(groupname = "strathE2E", shape = "dot", color = list(background = v[6], border = v[6],
                                              highlight = list(background = "white", border = v[6])))

```  
