---
title: "How do we group fishing gears?"
author: "Jack H Laverick, University of Strathclyde"
date: "07/01/2021"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

packages <- c("tidyverse", "exactextractr", "raster", "sf", "furrr", "patchwork") # List handy packages
lapply(c(packages), library, character.only = TRUE)                           # Load packages

source("./R scripts/@_Region file.R")                                         # Get region mask

plan(multiprocess)                                                            # Set up parallel processing

Region_mask <- st_transform(Region_mask, crs = 4326)                          # reproject to match EU data

domain <- st_transform(readRDS("./Objects/Domains.rds"), crs = 4326) %>%      # reproject to match EU data
  st_union() %>%                                                              # Create whole domain shape 
  st_as_sf() %>% 
  mutate(Keep = T)

#gear <- read.csv("./Data/MiMeMo gears.csv")                                   # Load fishing gear classifications

# Check the original gears for similarities
gear <- read.csv("./Data/MiMeMo gears.csv") %>%                               # Load fishing gear classifications
  dplyr::select(-Aggregated_gear) %>% 
  rename(Aggregated_gear = Gear_name)

guild <- read.csv("./Data/MiMeMo fish guilds.csv") %>%                        # Get guilds for FAO codes
  dplyr::select(FAO, Guild) %>% 
  rename(species = FAO) %>% 
  drop_na() %>% 
  distinct() %>%                                                              # Drop duplicated rows which hang around after ditching other systems
  group_by(species) %>%                                                       # 1 duplicated code to remove ()
  slice_head() %>%                                                            # So only take the first instance of each code
  ungroup()

GFW_mobile <- brick("./Objects/GFW.nc", varname = "NOR_mobile_gear") %>%      # Get mean fishing effort across years from Global fishing watch
  calc(mean, na.rm = T)  

GFW_static <- brick("./Objects/GFW.nc", varname = "NOR_static_gear") %>%      # For each class of gear
  calc(mean, na.rm = T)

 landings_target <- expand.grid(Guild = unique(guild$Guild), 
                                Aggregated_gear = unique(gear$Aggregated_gear))# Get combinations of gear and guild

EU_landings <- str_glue("./Data/EU fish/spatial_landings_{2015:2018}/") %>%   # Programmatically build folder names
  future_map(~{ rgdal::readOGR(.x) %>%                                        # Import each EU effort shapefile
                st_as_sf() %>%                                                # Convert to SF
                dplyr::select(year, ger_typ, rctngl_, species, ttwghtl, ttvllnd)}) %>% # Drop some columns, ttwghtl is "total weight landed",
  bind_rows() %>%                                                             # ttvllnd is "total value landed"
  rename(Gear_code = ger_typ)

EU_Arctic <- st_contains(Region_mask, EU_landings, sparse = F) %>%            # Which EU polygons are in the model mask?
  t() %>%                                                                     # Transpose to indicate row not columns
  EU_landings[.,] %>%                                                         # Subset the Eu data spatially
  rownames_to_column(var = "EU_polygon") %>% 
  left_join(gear) %>%                                                         # Attach gear classifications
  left_join(guild)                                                            # Attach guild classifications
  
```

## Outline

 We tried performing cluster analyses on landings by gear and guild from IMR, but saw no obvious patterns.
 We therefore need to make an informed choice when aggregating gears together as StrathE2E can only represent so many.
 Gears of specific management interest are easy to single out for inclusion, harpoons, rifles for seals etc.
 But there are some gears which we need to decide whether to combine.
 
 How different are different types of trawlers in terms of their landings by guild?
 This includes the distinction between mid-water and bottom trawling.
 
## EU landings in the Barents Sea

Do midwater trawls look different to bottom trawls in terms of the guilds they land?

```{r EU, echo=FALSE, warning=FALSE, message = FALSE, fig.align = 'center'}
#### Scale EU landings by the proportion of fishing effort according to GFW in the model domain ####

weights <- dplyr::select(EU_Arctic, EU_polygon, Gear_type) %>%                # Limit to information needed to calculate the proportion of fishing effort in the model domain
  split(f = as.factor(as.numeric(.$EU_polygon))) %>%                          # Isolate each shape for fast parallel processing
  future_map( ~{                                                              # In parallel
    mutate(.x, total = if_else(Gear_type == "Mobile",                         # If this is a mobile gear
                               exact_extract(GFW_mobile, .x, fun = "sum"),    # Get all mobile fishing effort from GFW, else static effort
                               exact_extract(GFW_static, .x, fun = "sum"))) %>% # This is the total effort to scale features to within a polygon
    st_intersection(domain) %>%                                               # Crop the polygons to the model domain
    mutate(feature = if_else(Gear_type == "Mobile",                           # Now count fishing effort again
                             as.numeric(exact_extract(GFW_mobile, ., fun = "sum")),       
                             as.numeric(exact_extract(GFW_static, ., fun = "sum")))) %>%  
    st_drop_geometry()}) %>%                                   # Drop geometry for a non-spatial join
  data.table::rbindlist() %>%                                                 # Bind into a dataframe
  mutate(GFW_Scale = feature/total) %>%                                       # Get the proportion of effort per polygon in the domain
  replace_na(list(GFW_Scale = 1)) %>%                                         # If there was no GFW activity in the polygon replace NA with 1 to not use this for scaling
  dplyr::select(GFW_Scale, EU_polygon)

#### Summarise landings by guild and gear and scale to domain area ####

EU_fingerprint <- st_drop_geometry(EU_Arctic) %>%
  left_join(weights) %>% 
  mutate(corrected_weight = ttwghtl * GFW_Scale) %>%                        # Scale features effort per gear by the proportion of GFW activity by gear type in the model domain 
  group_by(Aggregated_gear, Guild, year) %>% 
  summarise(corrected_weight = sum(corrected_weight, na.rm = TRUE)) %>% 
  summarise(corrected_weight = mean(corrected_weight, na.rm = TRUE)) %>% 
  ungroup() %>% 
  right_join(landings_target)

flag <- magick::image_transparent(magick::image_read("./Notes/EU flag.png"), color = "white")

plot <- ggplot(drop_na(EU_fingerprint)) + 
  geom_raster(aes(x=as.factor(Guild), y=Aggregated_gear, fill = log10(corrected_weight+1))) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = "Guild", y = "Gear", fill = "Landings (log tonnes)", subtitle = "Gear/Guild fingerprint from EU fishing data") 

cowplot::ggdraw() +
  cowplot::draw_plot(plot) +
  cowplot::draw_image(flag, x =0.32 , y = 0.42, scale = 0.15)

```

## Norway landings in the Barents Sea

Do midwater trawls look different to bottom trawls in terms of the guilds they land?

```{r Norway, echo=FALSE, warning=FALSE, message = FALSE, fig.align = "center"}
#### IMR fishing data ####

species <- data.table::fread("./Data/IMR/IMR species list.csv", sep = ',') %>%# Get species look up table
  rename(Species = Tall)

gear <- data.table::fread("./Data/IMR/codelist_gear.csv", sep = ';') %>%      # Get gear look up table
  rename(Gear = CODE)

guild <- read.csv("./Data/MiMeMo fish guilds.csv") %>%                        # Get guilds for FAO codes
  dplyr::select(IMR.code, Guild) %>% 
  rename(Species = IMR.code) %>% 
  drop_na() %>% 
  distinct() %>%                                                              # Drop duplicated rows which hang around after ditching other systems
  group_by(Species) %>%                                                       # 1 duplicated code to remove ()
  slice_head() %>%                                                            # So only take the first instance of each code
  ungroup()

IMR <- data.table::fread("./Data/IMR/logbookNOR_00to20_b.lst", sep = ';') %>% # Import IMR fishing data
  `colnames<-`(c("Year", "Month", "Day", "Gear", "Fishing_time", "Area_code", "Economic_zone", 
                 "Area_Norway", "Location_Norway", "Vessel_length", "Species", "Weight")) %>% # Set column names
  filter(Area_Norway %in% c(1:4, 10:18, 20:25)) %>%                           # Limit to areas of interest
  left_join(gear) %>%                                                         # Attach labels
  left_join(species) %>%                                                      # Attach labels
  mutate(Weight = Weight/1000)                                                # Convert Kg to tonnes

## Heatmap ##

IMR_fingerprint <- rename(IMR, Geartype = ENGLISH) %>%                           # Rename columns
  left_join(guild) %>% 
  group_by(Guild, Geartype) %>%                                           # Summarise landings over all time
  summarise(Landings_tonnes = sum(as.numeric(Weight))) %>% 
  ungroup %>% 
  drop_na()

flag <- magick::image_transparent(magick::image_read("./Notes/Norway flag.png"), color = "white")

plot <- ggplot(IMR_fingerprint) + 
  geom_raster(aes(x=as.factor(Guild), y=Geartype, fill = log10(Landings_tonnes+1))) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = "Guild", y = "Gear", fill = "Landings (log tonnes)", subtitle = "Gear/Guild fingerprint from IMR fishing data")

cowplot::ggdraw() +
  cowplot::draw_plot(plot) +
  cowplot::draw_image(flag, x =0.32 , y = 0.42, scale = 0.15)

```

## Decision

After looking at the above we came up with a system for aggregating gears based on the similarity of catch composition by guild, but also which gears we would like to be able to independently manipulate in the model. The scheme is shown below, and is also contained in a csv file to control aggregating the data across R scripts consistently. 

Gear_type is used with global fishing watch data as they onl provide a crude disaggregation of gears. Gear_code works with the data from IMR for Norway and STECF for the EU. Conveniently the systems don't conflict, as IMR uses a numeric code and STECF uses characters. 

** Note** Mid-water pair trawls ended up aggregated with *Trawls* as they only landed demersal species. Mid-water otter trawls were added to *Pelagic* as they also caught planktivores and migratory fish.

| Aggregated_gear | Gear_name                             | Gear_type | Gear_code |
|-----------------|---------------------------------------|----------:|----------:|
| Trawls          | Undefined trawl                       | Mobile    | 50        |
| Trawls          | Double trawl                          | Mobile    | 58        |
| Trawls          | Triple trawl                          | Mobile    | 59        |
| Trawls          | Beam trawl                            | Mobile    | 56        |
| Trawls          | Bottom trawl                          | Mobile    | 51        |
| Trawls          | Bottom otter trawl                    | Mobile    | OTB       |
| Trawls          | Bottom pair trawl                     | Mobile    | PTB       |
| Trawls          | Mid-water pair trawl                  | Mobile    | PTM       |
| Trawls          | Otter twin trawls                     | Mobile    | OTT       |
| Pelagic         | Mid-water otter trawl                 | Mobile    | OTM       |
| Pelagic         | Pelagic trawl                         | Mobile    | 53        |
| Pelagic         | Purse seine                           | Mobile    | 11        |
| Pelagic         | Pelagic trawl (pair)                  | Mobile    | 54        |
| Hooks           | Undefined hook gear                   | Static    | 30        |
| Hooks           | Other hook and line                   | Static    | 32        |
| Hooks           | Floating hooks                        | Static    | 31        |
| Gillnets        | Undefined net                         | Static    | 20        |
| Gillnets        | Gillnet (static)                      | Static    | 22        |
| Gillnets        | Gillnet (drifting)                    | Static    | 21        |
| Seines          | Undefined seine net                   | Mobile    | 10        |
| Seines          | Danish seine                          | Mobile    | 61        |
| Pots            | Pot                                   | Static    | 42        |
| Pots            | Pots                                  | Static    | FPO       |
| Dropped         | Other                                 | NA        | 80        |
| Dropped         | Unkown                                | NA        | NK        |
| Harpoons        | Harpoon and similar unspecified types | Mobile    | 70        |
| Rifles          | Rifle                                 | Mobile    | 73        |
| Kelp harvesting | Kelp harvesting                       | Mobile    | Seaweed   |
| Dredging        | Dredge                                | Mobile    | DRB       |
| Jigging         | Jigging                               | Mobile    | 33        |
| Shrimp trawl    | Shrimp trawl                          | Mobile    | 55        |
