---
title: "Is most fishing really inshore?"
author: "Jack H Laverick, University of Strathclyde"
date: "07/01/2021"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(raster)
library(magick)
```

## Outline

When creating our estimates of international fishing effort for the Barents Sea about 40% of activity was over the inshore silt habitat. This seemed surprising given that this zone represents only ~6% of our total model domain. It's worth checking whether most of the activity is inshore.

## Norwegian effort in the Barents Sea

Looks largely inshore to me.

```{r Norway, echo=FALSE, warning=FALSE, message = FALSE, fig.align = "center"}

NOR <- brick("./Objects/GFW.nc", varname = "NOR_mobile_gear") %>% 
  as.data.frame(xy = T, na.rm = T) %>% 
  pivot_longer(X1:X5, names_to ="Year", values_to = "Effort") %>% 
  mutate(Year = as.numeric(str_remove(Year, "X"))+2011) %>% 
  filter(Effort != 0)

plot <- ggplot(NOR) +
  geom_raster(aes(x=x, y=y, fill = Effort)) +
  viridis::scale_fill_viridis(trans = "log") +
  theme_void() +
  theme(panel.background = element_rect(fill = "Black"),
        legend.position = c(0.8, 0.3)) +
  facet_wrap(vars(Year)) +
  labs(title = "Mobile Norwegian Gear") +
  NULL

flag <- image_read("./Notes/Flag norway.png")

cowplot::ggdraw() +
  cowplot::draw_plot(plot) +
  cowplot::draw_image(flag, x =0.42 , y = -0.02, scale = 0.15)

```

## Russian effort in the Barents Sea

Still looks inshore, but with more activity around Svalbard when compared to the Norwegian vessels. 

```{r Russia, echo=FALSE, warning=FALSE, message = FALSE, fig.align = 'center'}

RUS <- brick("./Objects/GFW.nc", varname = "RUS_mobile_gear") %>% 
  as.data.frame(xy = T, na.rm = T) %>% 
  pivot_longer(X1:X5, names_to ="Year", values_to = "Effort") %>% 
  mutate(Year = as.numeric(str_remove(Year, "X"))+2011) %>% 
  filter(Effort != 0)

plot <- ggplot(RUS) +
  geom_raster(aes(x=x, y=y, fill = Effort)) +
  viridis::scale_fill_viridis(trans = "log") +
  theme_void() +
  theme(panel.background = element_rect(fill = "Black"),
        legend.position = c(0.8, 0.3)) +
  facet_wrap(vars(Year)) +
  labs(title = "Mobile Russian Gear") +
  NULL

flag <- image_read("./Notes/Flag russia.png")                         # Get a flag

cowplot::ggdraw() +                                                     # Drop flag onto plot
  cowplot::draw_plot(plot) +
  cowplot::draw_image(flag, x =0.42 , y = -0.02, scale = 0.15)

```

## EU effort in the Barents Sea

Not very much activity at all when it comes to thinking about international effort.

```{r EU, echo=FALSE, warning=FALSE, message = FALSE, fig.align = 'center'}

REST <- brick("./Objects/GFW.nc", varname = "REST_mobile_gear") %>%     # Import EU mobile fishing effort from GFW
  as.data.frame(xy = T, na.rm = T) %>%                                  # Convert rasters to dataframe
  pivot_longer(X1:X5, names_to ="Year", values_to = "Effort") %>%       # Collect years into 2 columns
  mutate(Year = as.numeric(str_remove(Year, "X"))+2011) %>%             # Create actual year
  filter(Effort != 0)                                                   # Drop pixels with no effort

plot <- ggplot(REST) +                                                  # Make background plot
  geom_raster(aes(x=x, y=y, fill = Effort)) +
  viridis::scale_fill_viridis(trans = "log") +
  theme_void() +
  theme(panel.background = element_rect(fill = "Black"),
        legend.position = c(0.8, 0.3)) +
  facet_wrap(vars(Year)) +
  labs(title = "Mobile EU Gear") +
  NULL

flag <- image_read("./Notes/Flag EU.png")                             # Get a flag

cowplot::ggdraw() +                                                     # Drop flag onto plot
  cowplot::draw_plot(plot) +
  cowplot::draw_image(flag, x = 0.42 , y = -0.02, scale = 0.15)

```

## Conclusion

I don't think the large proportion of effort over inshore silt is a bug. Previous figures I showed made it look like there was notable fishing activity in the offshore zone. Those figures only showed the presence of any activity, while these take the hours per pixel into account, giving a more representative picture.